A performance assessment of evolutionary algorithms in volunteer computing environments

### 2016-10-31 EvoPar2017/paper.tex
Anonymising References. Closes #130

Using this system for creating distributed experiments is called {\em
  volunteer}, {\em cycle-scavenging} or {\em opportunistic} computing
\cite{sarmenta2001volunteer} and it dates back, in different shapes
and underlying mechanisms, to the origin of the web \cite{david-seti:home}. Our interest
here, however, is to use it as a resource for evolutionary
computation, as our group has done for a long time \cite{jj-ppsn98}.

@@

Volunteer computing involves a user running a program voluntarily
and, as such, has been deployed in many different ways from the
beginning of the Internet, starting with the SETI@home framework for
processing extraterrestrial signals \cite{david-seti:home}. However
the dual facts of the introduction of JavaScript as a universal language for the
browser and the browser itself as an ubiquitous web and Internet client has
made this combination the most popular for volunteer computing
frameworks such as the one we are using here, and whose first version
was described in \cite{DBLP:conf/gecco/GuervosG15}.

@@

%
%
\begin{figure}[htbp]
\centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/zipf-1}

@@

This future work holds many challenges which once again will go in two
different directions: gathering more users and improving the
efficiency of the algorithm run in an asynchronous way by the
users. In the first case, it will be interesting to make it more {\em
  social} by comparing local performance to other's contributions, and
showing it in a graph or being able to tweet advances or the fact that
the solution has been found. Anything that keeps the users running the
system and attracts new users will contribute to the speed of finding
the solution. And the algorithm will have to be improved, mainly by
making the population more diverse. Right now there is a rigid policy
of contribution to the pool: send the best individual, but this could
be relaxed. Some other policies could also be tested, as well as
running heterogeneous algorithms in the same way that was done in
\cite{DBLP:journals/grid/ValdezTGVO15}. Diversity, as in any other
evolutionary algorithm, seems to be the key, but there are many ways of
approaching it.

@@

\bibliographystyle{splncs}
\bibliography{volunteer,GA-general,geneura,javascript,ror-js}

>>>>

Using this system for creating distributed experiments is called {\em
  volunteer}, {\em cycle-scavenging} or {\em opportunistic} computing
\cite{sarmenta2001volunteer} and it dates back, in different shapes
and underlying mechanisms, to the origin of the web \cite{david-seti:home}. Our interest
here, however, is to use it as a resource for evolutionary
computation, as it has been done for a long time \cite{jj-ppsn98anonymous}.

@@

Volunteer computing involves a user running a program voluntarily
and, as such, has been deployed in many different ways from the
beginning of the Internet, starting with the SETI@home framework for
processing extraterrestrial signals \cite{david-seti:home}. However
the dual facts of the introduction of JavaScript as a universal language for the
browser and the browser itself as an ubiquitous web and Internet client has
made this combination the most popular for volunteer computing
frameworks such as the one we are using here, and whose first version
was described in \cite{DBLP:conf/gecco/GuervosG15anonymous}.

@@

%
%
\begin{figure}[htbp]
\centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
%\includegraphics[width=\maxwidth]{figure/zipf-1}

@@

This future work holds many challenges which once again will go in two
different directions: gathering more users and improving the
efficiency of the algorithm run in an asynchronous way by the
users. In the first case, it will be interesting to make it more {\em
  social} by comparing local performance to other's contributions, and
showing it in a graph or being able to tweet advances or the fact that
the solution has been found. Anything that keeps the users running the
system and attracts new users will contribute to the speed of finding
the solution. And the algorithm will have to be improved, mainly by
making the population more diverse. Right now there is a rigid policy
of contribution to the pool: send the best individual, but this could
be relaxed. Some other policies could also be tested, as well as
running heterogeneous algorithms in the same way that was done in
\cite{DBLP:journals/grid/ValdezTGVO15anonymous}. Diversity, as in any other
evolutionary algorithm, seems to be the key, but there are many ways of
approaching it.

@@

\bibliographystyle{splncs}
\bibliography{volunteer,GA-general,geneura,javascript,ror-js,anonymous}
